Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-27 paper.tex
Add some conclusions for results

TODO

@@

TODO

>>>>

The memory overhead of \texttt{vm\_area\_struct}s increases linearly with the
number of mapped regions when these regions are separated by unused memory
addresses. When a workload maps a large number of regions, this overhead can be
of the order of hundreds of megabytes to gigabytes for large memory systems.  To
reduce this overhead, it is crucial that regions with similar access permissions
are placed adjacently in the address space so that they can be identified by a
single structure. It is important for large applications such as object-oriented
databases that map a large number of regions (TODO: Cite Linux book. Should we
mention this?)to be aware of these overheads and mitigate them.

@@

Transparent huge pages can consume a large fraction of memory and lead to early
onset of memory pressure when the workload accesses many pages that are
separated in its address space. The overhead of swapping greatly exceeds the
performance benefits provided by huge pages. As a result, the workload
performance can fall drastically in such cases. It might be advisable to
disable transparent huge pages for such applications. The kernel can also be
cautious and limit the allocation of huge pages to processes in order to
prevent early onset of memory pressure.
